Additional Analyses

### 2021-07-14 analyses_additional.Rmd
- implemented major changes after feedback from reviewers

# Additional analyses

## Privacy calculus
### Model 1

@@

### Model 2

@@

### Model 3

@@

### Model 4

@@

### Model 5

@@

## Effect of popularity cues
### Like vs. control

pri_con ~ a1*lik_ctrl
grats_spec ~ a2*lik_ctrl
self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl_simple, fit = TRUE, std = TRUE)
```

### Like & dislike vs. control

pri_con + grats_spec ~ likdis_ctrl
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl_simple, std = TRUE)
```

### Like & dislike vs. like

pri_con + grats_spec ~ likdis_lik
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, std = TRUE, fit = TRUE)
```

As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain the same.

## Privacy calculus
### Model "Peregistered"

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

self_dis_log ~ a1*pri_con + b1*grats_spec
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

## Effects of popularity cues
### Preregistered
#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
"
fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
"
fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
"

fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, fit = TRUE, std = TRUE)
```

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  self_dis_lg =~ self_dis_log

  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d_all$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)

# combine d with d factor scores
d_all %<>% cbind(select(d_fs, -version, -self_dis_log))
```

## Privacy calculus
### Model "Peregistered"

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

## Effects of popularity cues
### Preregistered

#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*lik_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_lik

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"

fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, fit = TRUE, std = TRUE)
```

>>>>

# Communication

In what follows, we report the results for the not-logged, that is the regular measure of communication.

## Model "Peregistered"

COMM ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
COMM + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

## Model "Adapted"

COMM ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

## Model "Simple"

COMM ~ a1*pri_con + b1*grats_spec

# Covariates
COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

# Preregistered Model

We first analyze the same models as before, but analyzing self-disclosure instead of communication. This was how we initially preregistered the study.

## Model "Peregistered"

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
```

## Model "Adapted"

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
```

## Model "Simple"

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
```

@@

As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain virtually the same.

### Model "Peregistered"

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
```

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
```

COMM_log ~ a1*pri_con + b1*grats_spec
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
```

```{r}
model_baseline <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider
  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
    SE01_01 ~~ x*SE01_02
    SE01_03 ~~ x*SE01_04
  comm_log =~ COMM_log

  COMM_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
"
fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
```

```{r}
# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(version = d_all$version, 
         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, COMM_log)

# combine d with d factor scores
d_all %<>% cbind(select(d_fs, -version, -COMM_log))
```

## Privacy calculus
## Model "Peregistered"

COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
COMM_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

## Model "Adapted"

COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

## Model "Simple"

COMM_log ~ a1*pri_con + b1*grats_spec

# Covariates
COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

# Alternative Models

## Model 1

@@

## Model 2

@@

## Model 3

@@

## Model 4

@@
